# Manual Chill Analysis

```{r, message=FALSE,echo= FALSE}
library(tidyverse)
library(chillR)
library(knitr)
library(pander)
library(kableExtra)
require(reshape2)
```


>
The `Winters_hours_gaps` data set has the columns: `Year`, `Month`, `Day`, `Hour`, `Temp_gaps`, `Temp`. First, the function `cleaned_data` is used to remove unnecessary columns such as `Temp_gaps()` from the data set.



```{r, echo=TRUE}

#Clean Function
cleaned_data = function(data_source) {
  data_source = 
    data_source[, c("Year", "Month", "Day", "Hour", "Temp")]
  return(data_source)
}

# Apply Function to Winters_hours_gaps
kable(head(cleaned_data(data_source = Winters_hours_gaps)),
      caption = "Cleaned  Dataset: Winters_hours_gaps")%>%
      kable_styling("striped", position = "left", font_size = 10)%>%
      scroll_box(width = "100%")
```




## Task 1

**Write a basic function that calculates warm hours (>25°C)**


```{r, echo = TRUE}
WH = function(hourtemps)
{
  hourtemps[, "warm_hours"] <- hourtemps$Temp >= 25.0
  return(hourtemps)
}
```


## Task 2

**Apply this function to the Winters_hours_gaps dataset**


```{r, echo=TRUE}
# have a look to the data set
kable(head(Winters_hours_gaps),caption = 
        "Example Dataset: Winters_hours_gaps")%>%
        kable_styling("striped", position = "left", font_size = 10)%>%
        scroll_box(width = "100%")
```


```{r,echo =TRUE}
# Apply Function
hourtemps = cleaned_data(data_source = Winters_hours_gaps)
kable(head(WH(hourtemps = hourtemps)))%>%
        kable_styling("striped", position = "left", font_size = 10)%>%
        scroll_box(width = "100%")
```


## Task 3

**Extend this function, so that it can take start and end dates as inputs and sums up warm hours between these dates**

```{r,echo =TRUE}
warm_hours_function = function(Input_Data,
                               S_Jahr,
                               S_Monat,
                               S_Tag,
                               S_Stunde,
                               E_Jahr,
                               E_Monat,
                               E_Tag,
                               E_Stunde) {
  Start_Date <-
    which(
      hourtemps$Year == S_Jahr & hourtemps$Month == S_Monat &
        hourtemps$Day == S_Tag &
        hourtemps$Hour == S_Stunde
    )
  End_Date <- which(
    hourtemps$Year == E_Jahr & hourtemps$Month == E_Monat &
      hourtemps$Day == E_Tag & hourtemps$Hour == E_Stunde
  )
  
  # Apply Function Warm Hours (WH)
  hourtemps = WH(hourtemps = Input_Data)
  
  # Calculate warm_hours
  warm_hours = sum(hourtemps$warm_hours[Start_Date:End_Date])
  
  return(cat("The number of heat hours is:", paste(warm_hours)))
}

warm_hours_function(
  Input_Data = hourtemps,
  S_Jahr = 2008,
  S_Monat = 5,
  S_Tag = 1,
  S_Stunde = 12,
  E_Jahr = 2008,
  E_Monat = 8,
  E_Tag = 31,
  E_Stunde = 12
)

```



