# Filling gaps in temperature records

## Task 1

**Use chillR functions to find out how many gaps you have in this dataset  (even if you have none, please still follow all further steps)**


```{r,echo=TRUE}

Leszno = read.csv("weather_data/Poland_leszno_chillR_weather.csv")

# detected many gaps 
Leszno_QC = fix_weather(Leszno)$QC

kable(Leszno_QC, caption = "Quality Check  for Data Leszno ") %>%
  kable_styling("striped", position = "left", font_size = 10) %>%
  scroll_box(width = "100%")
```

>
Upon closer examination, the seemingly promising location of Leszno exhibits many gaps in temperature data, particularly after 2005. These gaps must be filled with temperature data from neighboring stations.

## Task 2 

**Create a list of the 25 closest weather stations using the handle_gsod function**

```{r, echo = TRUE}
# station_list_close_to_leszno<-
#   handle_gsod(action="list_stations",location=c(16.57,51.85),time_interval=c(1990,2020))

# write.csv(station_list_close_to_leszno,"station_list_close_to_leszno.csv" )

station_list_close_to_leszno = read.csv("station_list_close_to_leszno.csv")

kable(station_list_close_to_leszno[1:10,], 
      caption="List of GSOD weather stations close to Leszno")%>%
  kable_styling("striped", position = "left", font_size = 10) %>%
  scroll_box(width = "100%")
```

## Task 3

**Identify suitable weather stations for patching gaps**

>
After reviewing the nearest weather stations to the Leszno location, KRZESINY, BABIMOST and LAWICA stations were identified as suitable for filling in the gaps in temperature data. These stations are ranked 4th, 6th and 7th on the list. All used locations have been plotted on the map.

```{r, echo=TRUE}

library(leaflet)
df <- data.frame(lat = c(52.332, 52.139, 52.421, 51.833),
                 lng = c(16.966, 15.799, 16.826, 16.533),
                 label = c("KRZESINY", "BABIMOST", "LAWICA", "LESZNO"))
m <- leaflet(width = "500px", height = "300px")
m <- addTiles(m)
m <- addMarkers(m, data = df, label = ~label, lat = ~lat, lng = ~lng,
                labelOptions = labelOptions(direction = "auto"))
m
```

## Task 4

**Download weather data for promising stations, convert them to chillR format and compile them in a list**


>
Weather data from the previously selected stations must now be downloaded. To avoid having to do this every time, the data is saved using the `save_temperature_scenario()` function and subsequently loaded using the `load_temperature_scenarios()` function. Afterwards, some statistics are used to determine the success of the data completion.

```{r, echo =TRUE}

# create a vector for looping
# positions_in_station_list<-c(4,6,7)

# create empty list 
# patch_weather<-list()



# for(i in 1:length(positions_in_station_list))
# {
#   patch_weather[[i]] <-
#     handle_gsod(
#       handle_gsod(
#         action = "download_weather",
#         location = station_list_close_to_leszno$chillR_code[positions_in_station_list[i]],
#         time_interval = c(1990, 2020)
#       )
#     )[[1]]$weather
#   names(patch_weather)[i] <-
#     station_list_close_to_leszno$STATION.NAME[positions_in_station_list[i]]
# }

# save result
# save_temperature_scenarios(patch_weather,"weather_data/gepatchtes_Wetter_PL", "patch_weather_pl")

#load result
patch_weather<-load_temperature_scenarios("weather_data/gepatchtes_Wetter_PL", "patch_weather_pl")
```




## Task 5

**Use the patch_daily_temperatures function to fill gaps**

>
The `patch_daily_temperatures()` function can be used to fill in missing data in the records of the starting weather station, in this case Leszno.

```{r, echo=TRUE}
# Fill in the gaps in Leszno and save in a new variable patched
patched<-patch_daily_temperatures(weather = Leszno,
                                  patch_weather = patch_weather)
```
>
Let's first look at the statistics in Table 9.3 Patches statistics for `KRZESNY`.
The table consists of two rows in total, `Tmin` and `Tmax`. The first column is called `mean_bias`. In Table 9.3, it shows `-0.931` for `Tmin` and `0.730` for `Tmax`. These numbers represent the average difference in mean temperature for daily maximum and minimum temperature, respectively, between the stations `Leszno` and `KRZESNY`. All data that is available for both stations is compared.
The `filled` column indicates how many days were filled with data from the auxiliary station. In this case, 5347 days were taken from the records of station `KRZESNY` and inserted into the dataset of station `Leszno`. The `gaps_remain` column shows how many gaps still exist.

```{r, echo = TRUE}

kable(patched$statistics[[1]],
      caption = paste("Patch statistics for",
                      names(patched$statistics)[1])) %>%
  kable_styling("striped", position = "left", font_size = 10) %>%
  scroll_box(width = "100%")


kable(patched$statistics[[2]],
      caption = paste("Patch statistics for",
                      names(patched$statistics)[2])) %>%
  kable_styling("striped", position = "left", font_size = 10) %>%
  scroll_box(width = "100%")


kable(patched$statistics[[3]],
      caption = paste("Patch statistics for",
                      names(patched$statistics)[3])) %>%
  kable_styling("striped", position = "left", font_size = 10) %>%
  scroll_box(width = "100%")
```

>
The `patch_daily_temperatures()` function allows the use of the arguments `max_mean_bias` and `max_stdev_bias`. These can be used to identify large temperature differences between the starting station and auxiliary station. For example, if these arguments are set to 1 °C for `max_mean_bias` and 2 °C `max_stdev_bias`, temperatures from the corresponding auxiliary station are only used if the deviation `from max_mean_bias` is less than or equal to 1 and `from max_stdev_bias` if the deviation is less than or equal to 2.

```{r, echo = TRUE}
# Fill in the gaps in Leszno and save in a new variable patched
# set max_mean_bias = 1 and max_stdev_bias = 2
patched<-patch_daily_temperatures(weather = Leszno,
                                  patch_weather = patch_weather,
                                  max_mean_bias = 1,
                                  max_stdev_bias = 2)
```

>
If we look at Table 9.4 Patch statistics for BABIMOST, we can see that no `Tmin` temperatures were used to fill in the `Leszno` dataset. The `mean_bias` in this example is `-1.114` and `stdev_bias` is `2.14`. The amount of both values is therefore greater than 1 and 2. The filled column, as expected, shows that no data was used to fill in the starting weather station `Leszno`.


```{r, echo =TRUE}
kable(patched$statistics[[1]],
      caption = paste("Patch statistics for",
                      names(patched$statistics)[1])) %>%
  kable_styling("striped", position = "left", font_size = 10) %>%
  scroll_box(width = "100%")


kable(patched$statistics[[2]],
      caption = paste("Patch statistics for",
                      names(patched$statistics)[2])) %>%
  kable_styling("striped", position = "left", font_size = 10) %>%
  scroll_box(width = "100%")


kable(patched$statistics[[3]],
      caption = paste("Patch statistics for",
                      names(patched$statistics)[3])) %>%
  kable_styling("striped", position = "left", font_size = 10) %>%
  scroll_box(width = "100%")

```
>
Finally, the `fix_weather()` function can be used to check how well the temperature dataset can be completed

```{r}
post_patch_stats<-fix_weather(patched)$QC


kable(post_patch_stats,
      caption = "Data completeness table for the weather record from
      Leszno, after applying the patch procedure") %>%
  kable_styling("striped", position = "left", font_size = 10) %>%
  scroll_box(width = "100%")

Leszno_weather_fix = fix_weather(patched)
#write.csv(Leszno_weather_fix$weather,"weather_data/Leszno_weather.csv")
```

